### 2021-08-17 sections/queueing_model/proportion_within_target/main.tex
Include alex check as a task

Another performance measure that is taken into consideration is the proportion 
of individuals whose waiting and service times lie within a specified 
time target \(t\).
Similar to section \ref{sec:waiting_time} three formulas are needed for this 
performance measure.

@@

The proportion of type 2 individuals within a time target:

>>>>

Another performance measure that is taken into consideration is the proportion 
of individuals whose waiting and service times are within a specified 
time target \(t\).
Similar to section \ref{sec:waiting_time} three formulas are needed for this 
performance measure.

@@

The proportion of type 2 individuals within a time target remains as:
